CIVILITY: Cloud based Interactive Visualization of Tractography Brain Connectome

### 2016-07-08 doc/spiePaper/article.tex

We apply our tractography pipeline to 19 infants (scanned at 1 year and 2 years approximately).
All data had previously been QC and registered in the same space : DWI space. The Middle surface is containing labels information according to the brain atlas AAL90.

The following section shows the results of this pipeline.

@@

Tractography 1year / 2year 
Nb voxel fitting
probtrack param
ROIs ignored
overlapping

Average

Variability

Main differents 1y/2y

	-- time of computation

	--

Results Matrix result / matrix computation / visualization

>>>>

We apply our tractography pipeline to 19 infants (scanned at 1 year and 2 years approximately).
All data had previously been QC and registered in the same space : DWI space. The Middle surface is containing labels information according to the brain atlas AAL90. 
The following section shows the results of this pipeline.

@@

We compute the brain connectome of these 19 infants at two ages : 1 year and 2 years. The tractography computed with FSL tools is using 2 tensors in the voxel fitting. The method of computation we have choosen is using surfaces as seeds. Each surfaces corresponds to a brain region in the atlas Automated Anatomical Labeling (AAL). All ROIs surfaces overlap on each others. The cerebellum regions is ignored in the brain connectome computation. The number of samples is set to 3000 (number of streamlines per voxel) with a step length of 0.75mm and a seed sphere sampling of 0.5.

We make some statistics on this dataset presented in the next section.

\subsection{Brain connectome average}

We compute the average of the brain connectome at each year (Figure 1 and Figure 2). We threshold the plotting between : 0.01 and 0.4 for a better visualization.
Figures 3 and 4 show the average of brain connectome on brain template with the same threshold.

%\begin{figure}
%\centering 
%\includegraphics[width=15cm]{average_1y.png}
%\caption[Average brain connectome at 2 year old]{Average brain connectome at 1 year old}
%\label{fig:AverageBrainConnectome1YearOld}
%\end{figure}

\begin{figure}
\centering 
\includegraphics[width=15cm]{average_2y.png}
\caption[Average brain connectome at 2 year old]{Average brain connectome at 2 year old}
\label{fig:AverageBrainConnectome2YearOld}
\end{figure}

%\begin{figure}
%\centering 
%\includegraphics[width=15cm]{average_brainTemplate_1y.png}
%\caption[Average brain connectome at 2 year old]{Average brain connectome at 2 year old}
%\label{fig:AverageBrainConnectome2YearOld}
%\end{figure}

\begin{figure}
\centering 
\includegraphics[width=15cm]{average_brainTemplate_2y.png}
\caption[Average brain connectome at 2 year old]{Average brain connectome at 2 year old}
\label{fig:AverageBrainConnectome2YearOld}
\end{figure}

Results show ....

\subsection{Variability of the brain connectome}

We compute the unbiased sample variance to ....

%\begin{figure}
%\centering 
%\includegraphics[width=15cm]{variability_1y.png}
%\caption[Variability of brain connectome at 2 year old]{Average brain connectome at 1 year old}
%\label{fig:VariabilityBrainConnectome1YearOld}
%\end{figure}

\begin{figure}
\centering 
\includegraphics[width=15cm]{variability_2y.png}
\caption[Variability brain connectome at 2 year old]{Average brain connectome at 2 year old}
\label{fig:VariabilityBrainConnectome2YearOld}
\end{figure}

\subsection{Observations}

The time of computation is higher for 2 year old subjects because of the size of the brain.
